%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'


\moderncvcolor{green}      


% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
%\usepackage{hyperref}

% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}


%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Georgia}{Tsambos}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
%\address{No 346,Manipay Road, Five Junction, Jaffna,SriLanka}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\cvref}[3][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \ifx&#3
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#3%
    \end{minipage}}\fi%
  \par\addvspace{#1}}
  

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-18mm}


\begin{center}
\begin{tabular}{ c c c c }
 \faLink\enspace gtsambos.github.io/ & \faEnvelopeO\enspace gtsambos@student.unimelb.edu.au
 %\\\faMobile\enspace +94 77 264 6761 & \faLinkedin\enspace in/sumanrbt97
\end{tabular}
\end{center}


\section*{Education}

{\customcventry{Aug 2017 -- Present}{University of Melbourne}{Doctor of Philosophy (Statistical Genetics)}{}{}{\begin{itemize}
\item Project title: 'A statistical study of genetic admixture and ancestry'
    \item Supervised by Damjan Vukcevic and Stephen Leslie at Melbourne Integrative\\ Genomics.
    \item Was confirmed in August 2018.
\end{itemize}
}

\vspace{3mm}  

{\customcventry{Feb 2015 -- Nov 2016}{University of Melbourne}{Master of Science (Statistics and Stochastic Processes)}{}{}{}{\begin{itemize}
%\item Specialisation: Statistics and Stochastic Processes.
    \item Completed with Distinction.
    \item Thesis work supervised by Damjan Vukcevic and Stephen Leslie.
  \end{itemize}}}
  
\vspace{3mm}  

{\customcventry{Mar 2009 -- Dec 2013}{University of New South Wales}{Bachelor of Advanced Mathematics (Hons) (Pure Mathematics)}{}{}{}{\begin{itemize}
  %  \item Major: Pure Mathematics.
    \item Honours project work in functional analysis and dynamical systems was\\ supervised by Gary Froyland and Cecilia Gonzalez-Tokman.
    \item  Received First Class Honours with a final mark of 91.
  \end{itemize}}}

\vspace{3mm} 
  
{\customcventry{Mar 2009 -- Dec 2012}{University of New South Wales}{Bachelor of Arts (Political Economy)}{}{}{}{}}

\vspace{3mm} 

\section{Recent professional activities}

\subsection{Paid roles}

{\customcventry{Feb 2017 - Feb 2018}{Melbourne Integrative Genomics, University of Melbourne}{Research assistant}{}{}{}{\begin{itemize}
    \item Helped to develop software pipelines for large-scale imputation of HLA\\ types in the Leslie lab.
\end{itemize}}}

\vspace{3mm} 

%{\customcventry{Feb 2017 - Jun 2017}{Research assistant}{Melbourne Integrative Genomics, University of Melbourne}{}{}{}{\begin{itemize}
%    \item Supervised by Damjan Vukcevic
%    \item Software pipelines for large-scale imputation
%\end{itemize}}}

\vspace{3mm} 

{\customcventry{Nov 2014 - Feb 2015}{Climate Change Research Centre, University of New South Wales}{Summer researcher}{}{}{}{\begin{itemize}
    \item Completed a project about the influence of soil moisture variability on\\ Australian climate extremes under the supervision of Dr Ruth Lorenz.
\end{itemize}}}

\vspace{3mm} 

{\customcventry{Feb 2013 - Nov 2014}{Faculties of Science and Engineering, UNSW}{Teaching assistant and sessional tutor}{}{}{}{
\begin{itemize}
\item SCIF1121, SCIF1131, MMAN3000, MATH1141
\item See 'Details of teaching roles' for more information.
\end{itemize}
 }}

\vspace{3mm} 

{\customcventry{Nov 2013 - Feb 2014}{Reserve Bank of Australia, Economic Research Division}{Summer cadet}{}{}{}{\begin{itemize}
    \item Completed a project about the relationship between home prices and\\ economic consumption/household spending.
    \item Helped write internal notes.
\end{itemize}}}

\vspace{3mm} 


\subsection*{Unpaid roles}

{\customcventry{Mar 2017 - present}{Statistical Society of Australia}{Young Statistician's Representative (Victoria)}{}{}{}{\begin{itemize}
    \item Organise all branch events targeted at members who are students or in the\\ early stages of their careers.
    \item Recent events have included networking evenings, the Young Statisticians\\ Showcase for graduate research, careers panels.
%    \item Handle private and public communications between the branch and young members.
\end{itemize}}}

\vspace{3mm} 

{\customcventry{May 2015 - present}{Statistics and Mathematics Postgraduate Society, Unimelb}{President, various other roles}{}{}{}{\begin{itemize}
\item Led and represented the society.
\item Oversaw the overall direction of the society's activities and events.
    \item Advocated for the interests and wellbeing of maths students to the 
    School\\ and the rest of the University.
\end{itemize}}}



\vspace{3mm} 

{\customcventry{Dec 2015 - May 2017}{Curious Minds}{Subject tutor}{}{}{}{\begin{itemize}
    \item Provided academic support and pastoral care.
    \item Curious Minds is a STEM-themed camp and academic program for high\\ school girls from rural, indigenous and low socio-economic backgrounds.
\end{itemize}}}

\vspace{3mm} 

{\customcventry{Mar 2011 - Mar 2012}{UNSW Mathematics Society}{Public Relations Officer}{}{}{}{\begin{itemize}
    \item Was responsible for communication between the society and its members.
    \item Maintained and monitored the society's social media pages.
\end{itemize}}}

\vspace{3mm} 

{\customcventry{Mar 2011 - Dec 2011}{The Shack, UNSW}{Subject tutor}{}{}{}{\begin{itemize}
    \item Taught Mathematics and Economics to local school students\\ from under-privileged backgrounds.
\end{itemize}}}

\vspace{3mm} 

 \section{Awards, prizes and scholarships}
 
 {\customcventry{Mar 2019}{School of Mathematics and Statistics, University of Melbourne}{Maurice Belz travel award}{}{}{
\begin{itemize}
\item Is funding my 2019 trip to the University of Oxford.
\end{itemize} 
 }}
 
 \vspace{3mm}

{\customcventry{Aug 2017 - present}{Australian Government}{Research Training Scheme Stipend}{}{}{%\begin{itemize}
%    \item Amount: \$ 25\thinspace 000 p.a.
%\end{itemize} 
}}

\vspace{3mm} 

{\customcventry{Dec 2016}{Statistical Society of Australia/ conference organisers}{EGJ Pitman Prize (runner up)}{}{}{\begin{itemize}
    \item For best student talk at the 2016 Australian Statistical Conference. 
    \item (Note: this is typically awarded to PhD students!)
\end{itemize} }}

\vspace{3mm} 

{\customcventry{Nov 2016}{Statistical Society of Australia}{Travel award}{}{}{\begin{itemize}
%  \item Amount: \$300.
    \item Funded my travel to the Australian Statistical Conference 2016. 
\end{itemize}}}

\vspace{3mm} 

{\customcventry{Jul 2015 - Nov 2016}{University of Melbourne}{Helen R Freeman scholarship}{}{}{
%\begin{itemize}
%\item Amount: \$20\thinspace000.
%    \item For prior academic performance.
%\end{itemize} 
%
}}

\vspace{3mm} 

{\customcventry{Nov 2011}{University of New South Wales}{Faculty of Science Vacation Research Scholarship}{}{}{\begin{itemize}
%\item Amount: \$700.
    \item Funded my research into matrix representations of Lie algebras under the supervision\\ of Prof. Michael Cowling.
\end{itemize} }}

\vspace{3mm} 

{\customcventry{Apr 2009 - Nov 2013}{University of New South Wales}{Faculty of Science Undergraduate Scholarship}{}{}{
%\begin{itemize}
%\item Amount: \$5000 p.a.
%    \item For academic achievement.
%\end{itemize} 
}}

\vspace{3mm} 

{\customcventry{2009}{University of New South Wales/Australian Government}{Various awards for High School Certificate results}{}{}{\begin{itemize}
    \item UNSW Scientia scholarship %(amount: \$10\thinspace000 p.a.)
    \item Australian Student Prize %(amount: \$1\thinspace000.)
    \item  UNSW Academic Achievement Prize %(amount: \$5\thinspace000).
\end{itemize} }}

\vspace{3mm} 


\section{Details of teaching roles}

{\customcventry{Jan 2019 - Feb 2019}{School of Mathematics and Statistics, University of Melbourne}{Undergraduate research supervisor}{}{}{}{
\begin{itemize}
\item Provided primary supervision for Zheng Fan's summer project.
\item Title: 'Meta-analysis with a general genetic model'
\end{itemize}
}
}

\vspace{3mm} 

{\customcventry{Feb 2013 - Nov 2014}{Faculties of Science and Engineering, UNSW}{Teaching assistant and sessional tutor}{}{}{}{
\begin{itemize}
\item Facilitated (lively!) class discussions and gave seminars in weekly 'lectorials'.
\item  Was the primary tutor in Advanced Science Seminar subjects, a compulsory\\ course that asks junior science students to consider the impact of science on\\ society (SCIF1121, SCIF1131, MMAN3000).
\item Was a first-year calculus class tutor (MATH1141).
\end{itemize}
 }}

\vspace{3mm} 

{\customcventry{Feb 2011 - Dec 2011}{The Shack, UNSW}{Subject tutor}{}{}{}{\begin{itemize}
    \item Taught HSC-level Mathematics and Economics to local school students\\ from under-privileged backgrounds.
\end{itemize}}}

\vspace{3mm} 
  
\section{Conferences and invited talks}
{\customcventry{Apr 2017}{Accounting for disease diversity in genetic association studies}{GeneMappers}{Geelong, Australia}{}{}{}
} 

\vspace{3mm} 

{\customcventry{Mar 2017}{International Women's Day: being a woman in science}{Berwick Grammar School}{Melbourne, Australia}{}{}{}
} 

\vspace{3mm} 

{\customcventry{Dec 2016}{Accounting for disease diversity in genetic association studies}{Australian Statistical Conference}{Canberra, Australia}{}{}{\begin{itemize}
    \item Was awarded the runner-up Pitman Prize for the best student talk.
\end{itemize}}
} 

\vspace{3mm} 


\section*{Professional affiliations}
{\customcventry{2019 - present}{Member}{Society for Molecular Biology and Evolution}{}{}{}{}{}
}

\vspace{3mm} 

{\customcventry{2016 - present}{Member}{Statistical Society of Australia}{}{}{}{}{}
}

\vspace{3mm} 

\setlength{\columnwidth}{\textwidth}
\addtolength{\columnwidth}{-\columnsep}
\setlength{\columnwidth}{.5\columnwidth}

\setlength{\hintscolumnwidth}{0.175\columnwidth}
\setlength{\separatorcolumnwidth}{0.025\columnwidth}
%
\renewcommand*{\recomputecvbodylengths}{%
  % body lengths
  \setlength{\maincolumnwidth}{\columnwidth-\leftskip-\rightskip-\separatorcolumnwidth-\hintscolumnwidth}%
  \setlength{\listitemcolumnwidth}{\maincolumnwidth-\listitemsymbolwidth}%
  \setlength{\doubleitemcolumnwidth}{\maincolumnwidth-\hintscolumnwidth-\separatorcolumnwidth-\separatorcolumnwidth}%
  \setlength{\doubleitemcolumnwidth}{0.5\doubleitemcolumnwidth}%
  \setlength{\listdoubleitemcolumnwidth}{\maincolumnwidth-\listitemsymbolwidth-\separatorcolumnwidth-\listitemsymbolwidth}%
  \setlength{\listdoubleitemcolumnwidth}{0.5\listdoubleitemcolumnwidth}%
  % regular lengths
  \setlength{\parskip}{0pt}}
\recomputecvbodylengths
 \section{References}
\begin{multicols}{2}
\cvref{Damjan Vukcevic}
  { Lecturer in Statistical Genomics \\ University of Melbourne\\ Melbourne, Australia}
 % {\faPhone \, +94 11 264 0422 (ext.:3315)}\\
  {\faEnvelopeO \, damjan.vukcevic@unimelb.edu.au}
  
\columnbreak

\cvref{Jerome Kelleher}
  {Senior Statistical Programmer \\ Big Data Institute, University of Oxford\\ Oxford, United Kingdom}
  {\faEnvelopeO \, jerome.kelleher@well.ox.ac.uk}
\end{multicols}



      

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
